### 2015-04-14 src/intro/intro.tex
Updated spelling mistakes in introduction

Because flagellar motion is limited to either tumbles – random reorientation movements – or runs, the pathway linking these flagella to the biochemical sensors consists of only a few steps. With the advent of more advanced sensory and motoric systems, both the amount of information available to drive behaviour as well as the amount of possible behaviours available increased tremendously. As direct biochemical links between perception and action were no longer sufficient, simple neural network evolved to process the sensory signals allowing for abstract decisions about movement. Because organisms became more complex, these networks evolved into a complete (central) nervous system, culminating in the cerebral cortex.

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{src/intro/figures/vestibular.pdf}
    \caption{Schematic view of the inner ear complex consisting of the auditory system (cochlea) and the vestibular system. The vestibular system has three angular velocity (semicircular canals) and two linear acceleration (saccule and utricle) sensors.}
    \label{intro:vestibular}
\end{figure}

@@

The semicircular canals measure the three-dimensional rotational velocity of the head. Each side of the head contains three orthogonally oriented canals allowing for rotation to be perceived in all three dimensions. Each of the six canals consists of a circular tube filled with a fluid known as endolymph (see \panelref{intro:fig:canals}{A}). One part of the tube, the ampulla, is a bit thicker than the rest and contains a membrane, the cupula, that separates the fluid. When the head rotates, the fluid stays behind because of its inertia which in turn causes the membrane to deflect (see \panelref{intro:fig:canals}{B}). While the inertial fluid motion suggests that the cupula should be sensitive to angular acceleration, reactive forces resulting from the fluid motion, such as endolymph viscosity and cupular elasticity,  cause the cupular deflection to reflect angular velocity instead \cite{goldberg2012}.

@@

The deflection of the cupula is transduced by special hair cells which are partially embedded in the cupula. These hair cells contain bundles of small protrusions, or hairs, on their apical surface. Each bundle contains several smaller stereocilia mechanically linked to one larger kinocilium \cite{pickles1984}. When the stereocilia are stretched towards the kinocilium the links cause cation channels (mechanoelectric transducers or METs) to open and the membrane to depolarize. Glutamate is then released into the synapse and causes the afferent neuron to depolarize and, after sufficient depolarizations, to generate action potentials \cite{purves2012}. These action potentials transmit the angular velocity sensed by the canals to the central nervous system through the  vestibulocochlear nerve.

@@

Einstein's equivalence principle states that  it is not possible to measure forces caused by linear acceleration and by gravity independently. The signal coming from the otoliths is therefore proportional to the combination of these forces \cite{fernandez1976b}, which is commonly referred to as the gravito-inertial force (GIF). Compared to the three semicircular canals, which are able to sense rotation in three dimensions due to their orthogonal organization, either side of the head only contains two otolith organs. It is still possible to sense the gravitoinertial force in three dimensions because the otolith organs are curved, and the orientation of the hair cells determined the direction of sensitivity \cite{goldberg2012}.

@@

For many actions, the brain needs to disentangle the contributions of gravity and linear acceleration to the gravitointertial force. For example, the linear vestibuloocular reflex (LVOR) that stabilizes gaze during translation should be sensitive to translation while ignoring gravity. Under normal circumstances, the brain is able to perform this task well \cite{merfeld1995}, but during extreme conditions such as in airplanes or space flight errors might occur. The somatogravic illusion \cite{glasauer1995} is an example of a disambiguation error. In this illusion an airplane accelerates forward which causes an inertial force in the opposite direction. The direction of the resulting GIF will therefore be in between gravity (downward) and the intertial force (backward). The brain erroneously interprets the (majority of the) GIF as being caused by gravity, leading to the perception of "nose-up" pitch tilt.

@@

Since then, the contribution of specific organs to GIF perception has been demonstrated. In 1992, \citeauthor{mittelstaedt1992} rotated supine participants along  their naso-occipital axis,  causing  the centrifugal force to act on somatic GIF sensors  but not on the otoliths. In nephrectomized participants, the perceived direction of gravity relied less on the centrifugal force compared to controls, suggesting that the kidneys play a crucial role in perception of the gravitointertial force. Further evidence came from Trousselard \citeyear{trousselard2004}, who showed that the perception of gravity in a tilted position depends on whether the stomach is full or empty. In addition, reducing somatosensory cues, by applying a body cast, also affects the perception of gravity \cite{trousselard2004}.  Similar results have been obtained for many other visceral factors, such as the blood vessels \cite{vaitl2002}, and spinal axis fluid \cite{vaitl1997}.

@@

\subsubsection{Vection}
When we move through the environment, the image of the world on our retina shifts. This large-field shift pattern, also known as optic flow, depends on the movement being made. Lateral translation (\figref{intro:fig:vection}A) for example causes a different pattern than roll rotation (\figref{intro:fig:vection}B). At the turn of the 19th century von Helmholtz \citeyear{vonhelmholtz1867} recognized the importance of these flow signals for self-motion perception. In some cases the optic flow signal is so strong that it causes a percept of self-motion in stationary participants, called vection \cite{dichgans1978}. This is experienced, for example, when sitting on the train and a neighbouring train starts to move. This effect is much less likely to occur when e.g. on the platform, suggesting that the vection signal is integrated with prior knowledge about the environment before causing self-motion perception \cite{andersen1985,lepecq1995}

@@

\subsubsection{Landmarks}
In addition to relative cues, the brain seems to use absolute cues in both the perception of gravity and self-motion. For the perception of gravity, it makes use of the fact that many lines within the world are aligned with either the horizon or gravity (\figref{intro:fig:treeframe}A). Straight lines therefore acts as a priors attracting the perceived direction of gravity towards them. A special case is the rod-and-frame illusion (\figref{intro:fig:treeframe}B), where the perceived angle of a rod relative to gravity is affected by the orientation of the frame that contains it \cite{witkin1948}.

@@

Similarly, our position within the world can be established using world-fixed landmarks. With the exception of animals and vehicles, most items in the world rarely change position. By comparing our current visual scene (e.g. Sequoia trees in \figref{intro:fig:treeframe}A) with our knowledge about the environment we can determine our location (in this case northern California). Because the experiments outlined in this thesis were performed in near darkness, these absolute navigational cues can be considered less relevant.

\subsubsection{Oculomotor}
Self-motion is typically accompanied by eye movements that help to improve dynamic visual acuity and reduce retinal slip. In Chapter 3 of this thesis, we explore whether these eye movements may have a reversed role, providing cues about self-motion perception beyond optic flow parsing.

In 1963, \citeauthor{guedry1963} reported a substantial underestimation of displacement when their observers watched a small body-fixed target compared to displacements in the dark. Because of the VOR, eye movement in darkness are larger than those in the body-fixed condition. The underestimation in the body-fixed condition can therefore be interpreted as the involvement of eye movements, although the authors did not suggest this 
Studies on postural sway also indicate a role of eye movement is self-motion perception. Making eye movements causes postural sway to increase, suggesting that eye movements influence self-motion perception \cite{glasauer2005,rodrigues2015}.

One complication is that the magnitude, $e$, of these eye movements not only depend on the translation amplitude, $T$, but also on the fixation depth, $d$. Oculomotor cues to depth include binocular vergence angle and accommodation, both most robust for less fixations than a meter or so away(ref). When fixating position $(x, d)$, the eye position at starting position is $e_0 = atan(d/x) \approx d/x$. By subtracting the eye position after the translation, $e_1 = atan(d/(x+T)) \approx d/(x+T)$, we obtain the eye movement amplitude, $e \approx d/T$. In Chapter 4 we explore whether the brain takes this geometry into account and compensates for fixation depth when using eye movements in self-motion perception. Fixation depth plays also a crucial role in chapter 5, in which the the effects of eye and head movements on spatial updating are investigated

@@

The vestibulo-ocular reflex (VOR) is driven by the short-latency vestibular signal and compensates for both rotation and translation of the head. The rotational and translational part of the VOR have their own dedicated reflex arcs. The translational VOR, or TVOR, is driven by the otolith signal while the rotational VOR, or RVOR, is mainly driven by the semicircular canals. The RVOR operates during head rotation by counter rotating the eyes in the opposite direction to the head. Because its gain is about one, eye velocity is about equal, but of opposite sign, to the head velocity \cite{goldberg2012}. The TVOR operates during head translation, when the head moves orthogonally to the line of sight. In contrast to the RVOR, the TVOR needs to take fixation depth into account. Simple geometry shows that the ideal TVOR response is inversely proportional to fixation distance, $e_{vor} = atan⁡(d/T)$. As a result, no compensatory eye movements are required when fixating targets at infinity to maintain a stable retinal image.

@@

While reflexes by definition depend on minimally processed sensory signals, higher animal functions can rely on more elaborate processing. One such processing step is determining the underlying physical cause of a sensory signal. Multiple sensory systems provide information about the same physical quantity. For example, both the visual and the vestibular system provide information about self-motion. Two very naive approaches to derive a self-motion percept from these signal whould be to solely rely on the most reliable cue and ignore the others or to just average the available signals. A better solution, however, is to weigh all available signals by their  relative reliabilities and combine them with a-priori knowledge about the probability of specific self-motion states. This approach is known as statistically optimal, or Bayesian, integration.

@@

From the point of view of the brain, the observations, $x_i$, are given while the stimulus, $x$, has to be inferred. In this case, probability $P(x_i│x)$ is referred to as the likelihood of  the  stimulus given the observations, or $\mathcal{L}(x|x_i)$. Given multiple sensory observations, $x_1,...,x_n$, we can now compute the likelihood of the stimulus:

\begin{equation}
\mathcal{L}(x|x_1,...,x_n) = P(x_1,...,x_n|x) = \prod_i P(x_i|x)
\end{equation}

@@

\begin{equation}
P(x|x_1,...,x_n) = \frac{P(x_1,...,x_n)P(x)}{P(x_1,...,x_n)}
\end{equation}

In this equation, $P(x)$ represents the prior probability of the stimulus, that is the probability of the stimulus occurring without taking the sensory input into account. The left-hand side of the equation, $P(x│x_1,..,x_n$, is commonly referred to as the posterior probability.

@@

\begin{equation}
\hat{x} = argmax_x P(x_1,...,x_n|x)P(x)
\label{intro:eq:map}
\end{equation}

@@

\begin{equation}
\hat{x} = argmax_x P(x_1,...,x_n|x)
\label{intro:eq:mle}
\end{equation}

@@

In many cases the brain does not use a flat prior, but a Gaussian one. For example, in Chapter 2, we use a prior ... that encodes the assumption that the head is mostly upright in space. In this case, the Gaussian prior can be seen as an additional sensory signal that is weighted into the posterior estimate.

@@

In addition to establishing perceptual equality, the 2AFC paradigm also allows for quanifying the uncertainty in perception by looking at the slope of the psychometric curve around the PSE. This uncertainty is commonly quantified by the standard deviation of the cumulative Gaussian probability distribution that underlies the responses of the subject, represented by the Greek letter sigma ($\sigma$).

%%%% Include some equations?

@@

\subsection{Subjective body tilt}
In the subjective body tilt, or SBT, task the perceived body orientation with respect to a given body tilt angle is probed. Participants are first given a reference angle, e.g. 45 \si{\degree}, and are then rotated to an angle close to the reference angle, e.g. 46 \si{\degree} (see \panelref{intro:fig4}{A}). They then have to indicate whether their current orientation is clockwise or counter-clockwise with respect to the reference angle. By systematically probing rotation angles around the reference angle we can obtain both the bias and uncertainty on the percept of body tilt.

@@

When seated straight this task, participants do not make any static errors and are very certain about their responses (see \panelref{intro:fig5}{B} and \hyperref[intro:fig5]{C}). This changes when tilting the participant before the task. In general, the static error increases with tilt angle. When the direction of the error is in the direction of the body mid-line, this effect is known as the Aubert or A-effect. At smaller angles overcompensation occurs and the static error is in the opposite direction, that is away from the body mid-line. This latter effect is known as the E-effect and could be due to the effects of ocular counter-roll (OCR).

@@

An accurate internal estimate of self-motion perception is not only crucial for navigation, but can also be used to updated memorized locations of previously seen objects. This is process in known as spatial updating. \Chapter{p2} presents the final experimental study of this thesis, where we investigate how self-motion signals are used in spatial updating. We show that the errors made during spatial updating do not only depend on the location of the previously seen object, but also on the location of gaze. This is consistent with spatial updating in a gaze-centred reference frame. We further show that the underestimation of self-motion is a possible cause of the errors found.

>>>>

Because flagellar motion is limited to either tumbles - random reorientation movements - or runs, the pathway linking these flagella to the biochemical sensors consists of only a few steps. With the advent of more advanced sensory and motoric systems, both the amount of information available to drive behaviour as well as the amount of possible behaviours available increased tremendously. As direct biochemical links between perception and action were no longer sufficient, simple neural network evolved to process the sensory signals allowing for abstract decisions about movement. Because organisms became more complex, these networks evolved into a complete (central) nervous system, culminating in the cerebral cortex.

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{src/intro/figures/vestibular.pdf}
    \caption{Schematic view of the inner ear complex consisting of the auditory system (cochlea) and the vestibular system. The vestibular system has three angular velocity (semicircular canals) and two linear acceleration (saccule and utricle) sensors. Image adapted from \protect\citeNP{gray1918}.}
    \label{intro:vestibular}
\end{figure}

@@

The semicircular canals measure the three-dimensional rotational velocity of the head. Each side of the head contains three orthogonally oriented canals allowing for rotation to be perceived in all three dimensions. Each of the six canals consists of a circular tube filled with a fluid known as endolymph (see \panelref{intro:fig:canals}{A}). One part of the tube, the ampulla, is a bit thicker than the rest and contains a membrane, the cupula, which separates the fluid. When the head rotates, the fluid stays behind because of its inertia which in turn causes the membrane to deflect (see \panelref{intro:fig:canals}{B}). While the inertial fluid motion suggests that the cupula should be sensitive to angular acceleration, reactive forces resulting from the fluid motion, such as endolymph viscosity and cupular elasticity,  cause the cupular deflection to reflect angular velocity instead \cite{goldberg2012}.

@@

The deflection of the cupula is transduced by special hair cells which are partially embedded in the cupula. These hair cells contain bundles of small protrusions, or hairs, on their apical surface. Each bundle contains several smaller stereocilia mechanically linked to one larger kinocilium \cite{pickles1984}. When the stereocilia are stretched towards the kinocilium the links cause cation channels (mechanoelectric transducers or METs) to open and the membrane to depolarise. Glutamate is then released into the synapse and causes the afferent neuron to depolarise and, after sufficient depolarisations, to generate action potentials \cite{purves2012}. These action potentials transmit the angular velocity sensed by the canals to the central nervous system through the vestibulocochlear nerve.

@@

Einstein's equivalence principle states that  it is not possible to measure forces caused by linear acceleration and by gravity independently. The signal coming from the otoliths is therefore proportional to the combination of these forces \cite{fernandez1976b}, which is commonly referred to as the gravito-inertial force (GIF). Compared to the three semicircular canals, which are able to sense rotation in three dimensions due to their orthogonal organization, either side of the head only contains two otolith organs. It is still possible to sense the gravito-inertial force in three dimensions because the otolith organs are curved, and the orientation of the hair cells determined the direction of sensitivity \cite{goldberg2012}.

@@

For many actions, the brain needs to disentangle the contributions of gravity and linear acceleration to the gravito-intertial force. For example, the linear vestibulo-ocular reflex (LVOR) that stabilizes gaze during translation should be sensitive to translation while ignoring gravity. Under normal circumstances, the brain is able to perform this task well \cite{merfeld1995}, but during extreme conditions such as in airplanes or space flight errors might occur. The somatogravic illusion \cite{glasauer1995} is an example of a disambiguation error. In this illusion an airplane accelerates forward which causes an inertial force in the opposite direction. The direction of the resulting GIF will therefore be in between gravity (downward) and the intertial force (backward). The brain erroneously interprets the (majority of the) GIF as being caused by gravity, leading to the perception of "nose-up" pitch tilt.

@@

Since then, the contribution of specific organs to GIF perception has been demonstrated. In 1992, \citeauthor{mittelstaedt1992} rotated supine participants along their naso-occipital axis, causing the centrifugal force to act on somatic GIF sensors  but not on the otoliths. In nephrectomised participants, the perceived direction of gravity relied less on the centrifugal force compared to controls, suggesting that the kidneys play a crucial role in perception of the gravito-intertial force. Further evidence came from Trousselard \citeyear{trousselard2004}, who showed that the perception of gravity in a tilted position depends on whether the stomach is full or empty. In addition, reducing somatosensory cues, by applying a body cast, also affects the perception of gravity \cite{trousselard2004}.  Similar results have been obtained for many other visceral factors, such as the blood vessels \cite{vaitl2002}, and spinal axis fluid \cite{vaitl1997}.

@@

\subsubsection{Vection}
When we move through the environment, the image of the world on our retina shifts. This large-field shift pattern, also known as optic flow, depends on the movement being made. Lateral translation (\panelref{intro:fig:vection}{A}) for example causes a different pattern than roll rotation (\panelref{intro:fig:vection}{B}). At the turn of the 19th century von Helmholtz \citeyear{vonhelmholtz1867} recognized the importance of these flow signals for self-motion perception. In some cases the optic flow signal is so strong that it causes a percept of self-motion in stationary participants, called vection \cite{dichgans1978}. This is experienced, for example, when sitting on the train and a neighbouring train starts to move. This effect is much less likely to occur when e.g. on the platform, suggesting that the vection signal is integrated with prior knowledge about the environment before causing self-motion perception \cite{andersen1985,lepecq1995}

@@

\subsubsection{Landmarks}
In addition to relative cues, the brain seems to use absolute cues in both the perception of gravity and self-motion. For the perception of gravity, it makes use of the fact that many lines within the world are aligned with either the horizon or gravity (\panelref{intro:fig:treeframe}{A}). Straight lines therefore acts as a priors attracting the perceived direction of gravity towards them. A special case is the rod-and-frame illusion (\panelref{intro:fig:treeframe}{B}), where the perceived angle of a rod relative to gravity is affected by the orientation of the frame that contains it \cite{witkin1948}.

@@

Similarly, our position within the world can be established using world-fixed landmarks. With the exception of animals and vehicles, most items in the world rarely change position. By comparing our current visual scene (e.g. Sequoia trees in \panelref{intro:fig:treeframe}{A}) with our knowledge about the environment we can determine our location (in this case northern California). Because the experiments outlined in this thesis were performed in near darkness, these absolute navigational cues can be considered less relevant.

\subsubsection{Oculomotor}
Self-motion is typically accompanied by eye movements that help to improve dynamic visual acuity and reduce retinal slip. In \Chapter{p3} of this thesis, we explore whether these eye movements may have a reversed role, providing cues about self-motion perception beyond optic flow parsing.

In \citeyearNP{guedry1963}, \citeauthor{guedry1963} reported a substantial underestimation of displacement when their observers watched a small body-fixed target compared to displacements in the dark. Because of the VOR, eye movement in darkness are larger than those in the body-fixed condition. The underestimation in the body-fixed condition can therefore be interpreted as the involvement of eye movements, although the authors did not suggest this 
Studies on postural sway also indicate a role of eye movement is self-motion perception. Making eye movements causes postural sway to increase, suggesting that eye movements influence self-motion perception \cite{glasauer2005,rodrigues2015}.

One complication is that the magnitude, $e$, of these eye movements not only depend on the translation amplitude, $T$, but also on the fixation depth, $d$. Oculomotor cues to depth include binocular vergence angle and accommodation, both most robust for less fixations than a meter or so away. When fixating position $(x, d)$, the eye position at starting position is $e_0 = \arctan(d/x) \approx d/x$. By subtracting the eye position after the translation, $e_1 = \arctan(d/(x+T)) \approx d/(x+T)$, we obtain the eye movement amplitude, $e \approx d/T$. In \Chapter{p4} we explore whether the brain takes this geometry into account and compensates for fixation depth when using eye movements in self-motion perception. Fixation depth plays also a crucial role in \Chapter{p2}, in which the the effects of eye and head movements on spatial updating are investigated.

@@

The vestibulo-ocular reflex (VOR) is driven by the short-latency vestibular signal and compensates for both rotation and translation of the head. The rotational and translational part of the VOR have their own dedicated reflex arcs. The translational VOR, or TVOR, is driven by the otolith signal while the rotational VOR, or RVOR, is mainly driven by the semicircular canals. The RVOR operates during head rotation by counter rotating the eyes in the opposite direction to the head. Because its gain is about one, eye velocity is about equal, but of opposite sign, to the head velocity \cite{goldberg2012}. The TVOR operates during head translation, when the head moves orthogonally to the line of sight. In contrast to the RVOR, the TVOR needs to take fixation depth into account. Simple geometry shows that the ideal TVOR response is inversely proportional to fixation distance, $e_{vor} = \arctan(d/T)$. As a result, no compensatory eye movements are required when fixating targets at infinity to maintain a stable retinal image.

@@

While reflexes by definition depend on minimally processed sensory signals, higher animal functions can rely on more elaborate processing. One such processing step is determining the underlying physical cause of a sensory signal. Multiple sensory systems provide information about the same physical quantity. For example, both the visual and the vestibular system provide information about self-motion. Two very naive approaches to derive a self-motion percept from these signal would be to solely rely on the most reliable cue and ignore the others or to just average the available signals. A better solution, however, is to weigh all available signals by their relative reliabilities and combine them with a-priori knowledge about the probability of specific self-motion states. This approach is known as statistically optimal, or Bayesian, integration.

@@

From the point of view of the brain, the observations, $x_i$, are given while the stimulus, $x$, has to be inferred. In this case, probability $P(x_i|x)$ is referred to as the likelihood of the stimulus given the observations, or $\mathcal{L}(x|x_i)$. Given multiple sensory observations, $x_1,\dotsc,x_n$, we can now compute the likelihood of the stimulus:

\begin{equation}
\mathcal{L}(x|x_1,\dotsc,x_n) = P(x_1,\dotsc,x_n|x) = \prod_i P(x_i|x)
\end{equation}

@@

\begin{equation}
P(x|x_1,\dotsc,x_n) = \frac{P(x_1,\dotsc,x_n)P(x)}{P(x_1,\dotsc,x_n)}
\end{equation}

In this equation, $P(x)$ represents the prior probability of the stimulus, that is the probability of the stimulus occurring without taking the sensory input into account. The left-hand side of the equation, $P(x|x_1,\dotsc,x_n$, is commonly referred to as the posterior probability.

@@

\begin{equation}
\hat{x} = \argmax_x P(x_1,\dotsc,x_n|x)P(x)
\label{intro:eq:map}
\end{equation}

@@

\begin{equation}
\hat{x} = \argmax_x P(x_1,\dotsc,x_n|x)
\label{intro:eq:mle}
\end{equation}

@@

In many cases the brain does not use a flat prior, but a Gaussian one. For example, in \Chapter{p1}, we use a prior that encodes the assumption that the head is mostly upright in space. In this case, the Gaussian prior can be seen as an additional sensory signal that is weighted into the posterior estimate.

@@

In addition to establishing perceptual equality, the 2AFC paradigm also allows for quantifying the uncertainty in perception by looking at the slope of the psychometric curve around the PSE. This uncertainty is commonly quantified by the standard deviation of the cumulative Gaussian probability distribution that underlies the responses of the subject, represented by the Greek letter sigma ($\sigma$).

@@

\subsection{Subjective body tilt}
In the subjective body tilt, or SBT, task the perceived body orientation with respect to a given body tilt angle is probed. Participants are first given a reference angle, e.g. 45\si{\degree}, and are then rotated to an angle close to the reference angle, e.g. 46\si{\degree} (see \panelref{intro:fig4}{A}). They then have to indicate whether their current orientation is clockwise or counter-clockwise with respect to the reference angle. By systematically probing rotation angles around the reference angle we can obtain both the bias and uncertainty on the percept of body tilt.

@@

When seated straight this task, participants do not make any static errors and are very certain about their responses (see \panelref{intro:fig5}{B} and \hyperref[intro:fig5]{C}). This changes when tilting the participant before the task. In general, the static error increases with tilt angle. When the direction of the error is in the direction of the body mid-line, this effect is known as the Aubert or A-effect. At smaller angles overcompensation occurs and the static error is in the opposite direction, which is away from the body mid-line. This latter effect is known as the E-effect and could be due to the effects of ocular counter-roll (OCR).

@@

An accurate internal estimate of self-motion perception is not only crucial for navigation, but can also be used to updated locations of previously seen objects. This is process in known as spatial updating. \Chapter{p2} presents the final experimental study of this thesis, where we investigate how self-motion signals are used in spatial updating. We show that the errors made during spatial updating do not only depend on the location of the previously seen object, but also on the location of gaze. This is consistent with spatial updating in a gaze-centred reference frame. We further show that the underestimation of self-motion is a possible cause of the errors found.
